### 2017-02-12 README.Rmd
Add CoC - addressing #39
link to vignettes from README, addressing #39

There are two experimental functions:

-  `vis_guess()` has a guess at what the value of each cell, using `readr::parse_guess`. This means that "10.1" will return "double", and `10.1` will return "double", and `01/01/01` will return "date". Keep in mind that it is a **guess** at what each cell is, so you can't trust this fully.

- `vis_compare()` compares two dataframes, displaying the differences.

>>>>

There are also experimental which are described in more detail in the [vignette: "Experimental Features of visdat](http://www.njtierney.com/visdat/articles/experimental_features.html).

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
